---
title: "R  tutorial 1: How to create beautiful plots using ggplot2"
output: html_document
date: '2022-04-16'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE, cache = TRUE)
```

Codebook for example dataset:

Indomethacin RCT to prevent PEP Dataset [https://htmlpreview.github.io/?https://github.com/higgi13425/medicaldata/blob/master/man/codebooks/indo_rct_codebook.html]

Blood Storage [https://www.causeweb.org/tshs/datasets/Blood%20Storage%20Data%20Dictionary.pdf]

COVID-19 Testing Dataset [https://htmlpreview.github.io/?https://github.com/higgi13425/medicaldata/blob/master/man/codebooks/covid_testing_codebook.html]

Case-control Cancer Dataset [https://htmlpreview.github.io/?https://github.com/higgi13425/medicaldata/blob/master/man/codebooks/esoph_ca_codebook.html]

Obstetrics and Periodontal Therapy
Data Dictionary [https://www.causeweb.org/tshs/datasets/OPT_Data_Dictionary.pdf]

cath(dev) [https://htmlpreview.github.io/?https://github.com/higgi13425/medicaldata/blob/master/man/codebooks/cath_codebook.html] 3504 patients

```{r}
# load data we will use
#install.packages("medicaldata")
library(medicaldata)
#data(package = "medicaldata")
names(blood_storage)
names(indo_rct)
names(covid_testing)
names(esoph_ca)
names(opt)

library(dplyr)
library(magrittr)
data1 <- blood_storage %>% 
  janitor::clean_names()

# load package
library(ggplot2)
```

## Costumize legend title, label and color

```{r}

scale_fill_manual('Test Result', ## define legend title 
                    values = c('Invalid' = '#1f77b4', ## define legend color
                               'Negative' = '#e377c2', 
                               'Positive' = '#2ca02c')) + 

```

# One group

## Histogram Plot

StatBin requires a continuous x variable

```{r}
# most effective way is to modify the legend label in datafra
data1 %>% 
  mutate(t_stage = ) %>% 
  ggplot(aes(x = age,
         fill = factor(t_stage))) +
  geom_histogram(binwidth = 2, 
                 color = 'gray') +
  labs(x = 'Age',
       y = 'Frequency',
       title = 'Histogram of Age',
       fill = 'Clinical T 	Stage') + # most reliable way to define the legend title
  theme_bw()  
 

  
  
  # xlab('Age') +
  # ylab('Frequency') +
  # ggtitle('Histogram of Age')
```

## Density Plot

## Scatter Plot

# Two groups


# Three groups



# Multiple groups




